Silica-based integrated 1$\times$4 polarization beam splitter module for free-space BB84 quantum key distribution

### 2017-09-04 manuscript.tex
pseudo-random was modified to random

% 그러나 추가의 실험을 통해서
\subsection{QKD Test}
%B84 테스트베드의 Bob 파트에 장착하여 key 전송 실험을 수행했다.
The free-space BB84 test was performed with the fabricated module replacing the four polarization splitting block on the Bob's part of the test-bed, as shown in Fig. \ref{fig:testbed}.
\begin{figure}
  \centering
  \includegraphics[width=13cm]{testbed3.pdf}
  \caption{Setup for evaluating the integrated PBS module in the Bob part of a free-space QKD system. The module replaced one BS, one HWP, and two PBSes. Attn.: attenuator, DM: dichroic mirror, Sync. Laser: synchronization laser, M: mirror, Sync. Detector: synchronization detector, PC: polarization controller, SPD: single photon detector, FPGA: field-programmable gate array}
  \label{fig:testbed}
\end{figure}
%%% 수신부 테스트 조건 %%%
% 100MHz로 클럭을 발생시켰고, 두 개의 난수 발생기를 이용하여 네 개의 LD 중 하나로부터 빛을 100MHz의 주파수로 발생시켰다.
In the Alice's part, two pseudo-random number generators were used to choose the basis and binary data, and one of the four LDs emitted light accordingly at the clock rate of 100 MHz.
% LD로부터의 빛은 PBS, BS를 통해 동일한 경로가 되도록 했고, ND 필터로 펄스당 0.1개의 광자 레벨이 되도록 감쇄시켰다.
Collimated light from the four LDs transmitted  through the bulk optic PBS, BS, and HWP, and was finally attenuated to mean photon number of 0.1 per pulse by a neutral density filter.
LD signal with wavelength of 1550 nm was transmitted through dichroic mirror with quantum signal for synchronization of Alice and Bob.
% Bob 시스템에서는 collimation lens 를 통해 들어온 빛을 광섬유에 결합시켰고, 광섬유 편광조절기를 사용하여 편광 모듈의 칩으로 들어간 빛의 편광이 원래의 편광이 되도록 조절하였다.
In the Bob part, the light from Alice was  focused by a lens and coupled to an SMF.
The SMF and our integrated PBS module was connected via a PC that could recover the polarization of the light entering the PBS chip to the original one that Alice sent.
% 편광 모듈의 출력 쪽 네 개의 광섬유는 각각 단일광자 검출기에 연결하였다.
Each PMF on the output side of the PBS module was connected to a single photon detector.
% 테스트베드 구동 결과 overall QBER은 2.8%, sifted key rate 은 ___ kbps가 얻어졌다.
As a result of the test-bed operation, overall QBER of 2.81\% and sifted key rate of 415 kbps were achieved, as shown in Fig. \ref{fig:QKD_result}.
\begin{figure}[ht]
  \centering
  \includegraphics[height=5.6cm]{QKD_result}
  \caption{Test result for the PBS module in a free-space BB84 protocol test-bed at the clock rate of 100 MHz. (a) Raw key rate and sifted key rate for 100 sec and (b) QBER of four channels and overall QBER for 100 sec.}
  \label{fig:QKD_result}
\end{figure}
% 편광 모듈 대신 벌크 옵틱스를 사용했을 때는 QBER과 sifted key rate은 각각 __%와 ___kbps였다.
When bulk optic components were used instead of our PBS module, QBER and sifted key rate were measured to be 0.69\% and 1.56 Mbps, respectively.
% 두 경우의 차이는 대부분 편광 모듈에서의 손실에서 기인한다고 할 수 있다.
The difference between the two cases is attributable to relatively high optical loss and low PER of our PBS module compared to the bulk optic components.
% ___ dB의 손실은 이상적으로는 ___%의 QBER을 유발한다.
%In ideal case optical loss of \underline{23903} dB corresponds to QBER of \underline{2392}\%.
MZI-based PBS chips for 1.55 $\mu$m wavelength generally show better PER than the chip developed in this work \cite{Hashizume:2015ta}.
MZI works on the basis of phase relation that is determined by physical lengths of the two arms.
As the operation wavelength in this study is about half of that of optical telecommunication application, the performance of the MZI structure is more sensitive to small change in optical path length, and design optimization is more difficult.
Thus PER can be further improved by either optimizing the chip design with finer length variation or adopting smaller birefringence in BRW.

>>>>

% 그러나 추가의 실험을 통해서
\subsection{QKD Test}
%B84 테스트베드의 Bob 파트에 장착하여 key 전송 실험을 수행했다.
The free-space BB84 test was performed with the fabricated module replacing the four polarization splitting block on the Bob's part of the test-bed, as shown in Fig. \ref{fig:testbed}.
\begin{figure}
  \centering
  \includegraphics[width=13cm]{testbed3.pdf}
  \caption{Setup for evaluating the integrated PBS module in the Bob part of a free-space QKD system. The module replaced one BS, one HWP, and two PBSes. Attn.: attenuator, DM: dichroic mirror, Sync. Laser: synchronization laser, M: mirror, Sync. Detector: synchronization detector, PC: polarization controller, SPD: single photon detector, FPGA: field-programmable gate array}
  \label{fig:testbed}
\end{figure}
%%% 수신부 테스트 조건 %%%
% 100MHz로 클럭을 발생시켰고, 두 개의 난수 발생기를 이용하여 네 개의 LD 중 하나로부터 빛을 100MHz의 주파수로 발생시켰다.
In the Alice's part, two random number generators were used to choose the basis and binary data, and one of the four LDs emitted light accordingly at the clock rate of 100 MHz.
% LD로부터의 빛은 PBS, BS를 통해 동일한 경로가 되도록 했고, ND 필터로 펄스당 0.1개의 광자 레벨이 되도록 감쇄시켰다.
Collimated light from the four LDs transmitted  through the bulk optic PBS, BS, and HWP, and was finally attenuated to mean photon number of 0.1 per pulse by a neutral density filter.
LD signal with wavelength of 1550 nm was transmitted through dichroic mirror with quantum signal for synchronization of Alice and Bob.
% Bob 시스템에서는 collimation lens 를 통해 들어온 빛을 광섬유에 결합시켰고, 광섬유 편광조절기를 사용하여 편광 모듈의 칩으로 들어간 빛의 편광이 원래의 편광이 되도록 조절하였다.
In the Bob part, the light from Alice was  focused by a lens and coupled to an SMF.
The SMF and our integrated PBS module was connected via a PC that could recover the polarization of the light entering the PBS chip to the original one that Alice sent.
% 편광 모듈의 출력 쪽 네 개의 광섬유는 각각 단일광자 검출기에 연결하였다.
Each PMF on the output side of the PBS module was connected to a single photon detector.
% 테스트베드 구동 결과 overall QBER은 2.8%, sifted key rate 은 ___ kbps가 얻어졌다.
As a result of the test-bed operation, overall QBER of 2.81\% and sifted key rate of 415 kbps were achieved, as shown in Fig. \ref{fig:QKD_result}.
\begin{figure}[ht]
  \centering
  \includegraphics[height=5.6cm]{QKD_result}
  \caption{Test result for the PBS module in a free-space BB84 protocol test-bed at the clock rate of 100 MHz. (a) Raw key rate and sifted key rate for 100 sec and (b) QBER of four channels and overall QBER for 100 sec.}
  \label{fig:QKD_result}
\end{figure}
% 편광 모듈 대신 벌크 옵틱스를 사용했을 때는 QBER과 sifted key rate은 각각 __%와 ___kbps였다.
When bulk optic components were used instead of our PBS module, QBER and sifted key rate were measured to be 0.69\% and 1.56 Mbps, respectively.
% 두 경우의 차이는 대부분 편광 모듈에서의 손실에서 기인한다고 할 수 있다.
The difference between the two cases is attributable to relatively high optical loss and low PER of our PBS module compared to the bulk optic components.
% ___ dB의 손실은 이상적으로는 ___%의 QBER을 유발한다.
%In ideal case optical loss of \underline{23903} dB corresponds to QBER of \underline{2392}\%.
MZI-based PBS chips for 1.55 $\mu$m wavelength generally show better PER than the chip developed in this work \cite{Hashizume:2015ta}.
MZI works on the basis of phase relation that is determined by physical lengths of the two arms.
As the operation wavelength in this study is about half of that of optical telecommunication application, the performance of the MZI structure is more sensitive to small change in optical path length, and design optimization is more difficult.
Thus PER can be further improved by either optimizing the chip design with finer length variation or adopting smaller birefringence in BRW.
